# Analysis by Author Affiliation

Bar charts to examine how contribution to conferences have changed over time. 

```{r}
#spec(cpdata)

affildata <- cpdata %>%
  select_if(is.numeric) %>%
  gather(key = Affiliation, value = count, Academic:Private) %>%
  filter(count > 0) %>%
  group_by(`Affiliation`) %>%
  summarise_all(sum, na.rm=T) 
```

## Total Conference Contributions

Quick observations:

- Academic contributors dominate, followed by Government (but as shown above, Government contributions have decreased recently, replaced by NGOs)

```{r}

print(affildata %>%
    select(Affiliation, count) %>%
    mutate(prop = count/sum(count)) %>%
    mutate(prop = round(prop,3)))
    

ggplot(affildata, aes(x=Affiliation, y=count)) + 
  geom_bar(stat="identity") + 
  geom_text(aes(x=Affiliation, y=max(count), label = paste0(round(100*count / sum(count),1), "%"), vjust=-0.5))


```

## Landscape Type 

Stacked bar plots of contributions (by types and author affiliation)

### Using all landscape types

Quick observations:

- Business not good at reporting landscape type!
- Private have greatest proportions of Seascape and Other

```{r}
lspCounts <- affildata %>%
  select(`Affiliation`,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape, `Undefined LspType`,Other) %>%
  mutate(Asum = rowSums(.[2:8])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -`Affiliation`, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

print(affildata %>%
  select(`Affiliation`,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape, `Undefined LspType`,Other) %>%
  mutate(sum = rowSums(.[2:8])) %>%   #calculate total
  mutate_if(is.numeric, funs(prop = ./ sum))
)

ggplot(lspCounts, aes(x=`Affiliation`, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(lspCounts, aes(x=`Affiliation`, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")
```

### Without 'Undefined LspType' and 'Other' landscape types

Quick observations:

- Government has greatest proportion of Upland Rural
- Business has greatest Urban proportion and smallest Lowland Rural proportion
- Academic dominates total number of all landscape types (with possible exception of Upland Rural)

```{r}

lspCounts <- affildata %>%
  select(`Affiliation`,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape) %>%
  mutate(Asum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -`Affiliation`, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(lspCounts, aes(x=`Affiliation`, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(lspCounts, aes(x=`Affiliation`, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```



## Species

Quick observations

- Academic seem to be majority by absolute number for all species
- Business and Private have greatest proportions of Generic Habitat
- NGOs have greatest proportion of Birds (RSPB?)

```{r}

speciesCounts <- affildata %>%
  select(`Affiliation`,Mammals, Humans, Birds, Reptiles, Inverts, Plants, Amphibians, Fish, `Generic Habitat`,`Woodland Forests`) %>%
  mutate(Asum = rowSums(.[2:11])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -`Affiliation`, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(speciesCounts, aes(x=`Affiliation`, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(speciesCounts, aes(x=`Affiliation`, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```


## Methods

Quick observations

- Academic seem to be majority by absolute number for all methods
- Business obviously lower proportion of empirical studies (expensive?), substituted by GIS and qualitative
- Government has smallest proportion of qualitative
- Private has greatest proprtion of theoretical, no RS and relatively little GIS (technical training?)


```{r}

methodsCounts <- affildata %>%
  select(`Affiliation`,Empirical, Theoretical, Qualitative, Quantitative, GIS, `Remote sensing`) %>%
  mutate(Asum = rowSums(.[2:7])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -`Affiliation`, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(methodsCounts, aes(x=`Affiliation`, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(methodsCounts, aes(x=`Affiliation`, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Spatial Extent

Quick observations

- Academic seem to be majority by absolute number for all extents
- Business have largest proportion of Global and National studies, with smallest proprtion of Local studies
- Private has larest proportion of Local and Mini studies (cost-related and given no RS and few GIS studies?)
- Academic: decreasing proportion Local -> Regional -> National -> Global
- Government: greater proportion of National than Regional

```{r}

spatialCounts <- affildata %>%
  select(`Affiliation`,Micro, Mini, Local, Regional, National, Continental, Global,`Undefined Extent`) %>%
  mutate(Asum = rowSums(.[2:9])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -`Affiliation`, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(spatialCounts, aes(x=`Affiliation`, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(spatialCounts, aes(x=`Affiliation`, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Temporal Extent

Quick observations

- Vast majority of all affiliations did not list temporal extent of the study
Academic seem to be majority by absolute number for all methods
- Not much more of interest here...

```{r}

temporalCounts <- affildata %>%
  select(`Affiliation`,Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer, `Undefined Temporal`) %>%
  mutate(Asum = rowSums(.[2:10])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -`Affiliation`, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(temporalCounts, aes(x=`Affiliation`, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(temporalCounts, aes(x=`Affiliation`, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Concepts

Quick observations

- Academic seem to be majority by absolute number for all extents
- Business have greatest proportions of climate change and ecosystem services, less interested in history and legacy
- All other affiliations reasonably similar in terms of proportions

```{r}

conceptCounts <- affildata %>%
  select(`Affiliation`,`PPS of landscapes`,
`Connectivity and fragmentation`, `Scale and scaling`,`Spatial analysis and modeling`,LUCC,`History and legacy`,`Climate change interactions`,`Ecosystem services`,`Landscape sustainability`,`Accuracy and uncertainty`) %>%
  mutate(Asum = rowSums(.[2:11])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -`Affiliation`, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(conceptCounts, aes(x=`Affiliation`, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(conceptCounts, aes(x=`Affiliation`, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Other Concepts

Quick observations

- Academic seem to be majority by absolute number for all extents
- Government and NGOs have greater proportion of Management and Conservation than Academic
- Private low on biodiversity but higher on cultural landscapes, landscape assessment and planning

```{r}

otherCounts <- affildata %>%
  select(`Affiliation`,`Green Infrastructure`,`Planning and Architecture`,`Management and Conservation`,`Cultural Landscapes`,`Socio-economic Dimensions`,Biodiversity,`Landscape Assessment`,`Catchment Based Approach`,`Invasives Pests Diseases`) %>%
  mutate(Asum = rowSums(.[2:10])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -`Affiliation`, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(otherCounts, aes(x=`Affiliation`, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(otherCounts, aes(x=`Affiliation`, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

