# Analysis by Species

Bar charts to examine how contribution to conferences have changed over time.

## Total Conference Contributions

```{r}
#spec(cpdata)

sppdata <- cpdata %>%
  select_if(is.numeric) %>%
  gather(key = SppType, value = count, Mammals:Fish) %>%
  filter(count > 0) %>%
  group_by(`SppType`) %>%
  summarise_all(sum, na.rm=T) 
```

Quick observations:

- Amphibians, Fish, Reptiles are little studied

```{r}

AsppCounts <- sppdata %>%
  select(SppType,Academic, Government,NGO,Business,Private) %>%
  mutate(Asum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -SppType, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(AsppCounts, aes(x=SppType, y=count)) + geom_bar(stat="identity")

```

## Author Affiliation

Quick observations:

- Businesses and private individuals study humans (proportional)
- By absolute numbers NGOs dominate study of birds 

```{r}
ggplot(AsppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(AsppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```


## Landscape Type 

### Using all landscape types

Quick observations: 

- Human studies are most evenly distributed across landscape types
- Unsurprisingly, fish are studies in riverscapes and seascapes
- Birds, plants and inverts studies dominated by Lowland rural studies

```{r}
lspsppCounts <- sppdata %>%
  select(SppType,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape, `Undefined LspType`,Other) %>%
  mutate(Asum = rowSums(.[2:8])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -SppType, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(lspsppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(lspsppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")
```

### Without 'Undefined LspType' and 'Other' landscape types

Quick observations:

- Government has greatest proportion of Upland Rural
- Business has greatest Urban proportion and smallest Lowland Rural proportion
- Academic dominates total number of all landscape types (with possible exception of Upland Rural)

```{r}

lspsppCounts <- sppdata %>%
  select(SppType,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape) %>%
  mutate(Asum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -SppType, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(lspsppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(lspsppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```
