# Analysis by Organism

Bar charts to examine how contributions to conferences vary by organism

## Total Conference Contributions

```{r}
#spec(cpdata)

sppdata <- cpdata %>%
  select_if(is.numeric) %>%
  gather(key = SppType, value = count, Mammals:Fish) %>%
  filter(count > 0) %>%
  group_by(`SppType`) %>%
  summarise_all(sum, na.rm=T) 
```

Quick observations:

- Amphibians, Fish, Reptiles are little studied

```{r}

sppdata %>%
  select(SppType, count) %>%
  mutate(prop = count/sum(count)) %>%
  mutate(prop = round(prop,3)) %>% 
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")
    

ggplot(sppdata, aes(x=SppType, y=count)) + 
  geom_bar(stat="identity") + 
  geom_text(aes(x=SppType, y=max(count), label = paste0(round(100*count / sum(count),1), "%"), vjust=-0.25))

```

## Author Affiliation

Quick observations:

- Businesses and private individuals study humans (proportional)
- By absolute numbers NGOs dominate study of birds 

```{r}

authorCounts <- sppdata %>%
  select(SppType,Academic, Government,NGO,Business,Private) %>%
  mutate(sum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -SppType, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

ggplot(authorCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(authorCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```


## Landscape Type 

### Using all landscape types

Quick observations: 

- Human studies are most evenly distributed across landscape types
- Unsurprisingly, fish are studies in riverscapes and seascapes
- Birds, plants and inverts studies dominated by Lowland rural studies

```{r}
lspCounts <- sppdata %>%
  select(SppType,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape, `Undefined LspType`,Other) %>%
  mutate(sum = rowSums(.[2:8])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -SppType, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

ggplot(lspCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(lspCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")
```

### Without 'Undefined LspType' and 'Other' landscape types

Quick observations:

- Birds, Plants and Mammals studies predominantly in Lowland Rural lsps
- Plants studies are greatest contribution (in total number) to Upland Rural lsps  

```{r}

lspCounts <- sppdata %>%
  select(SppType,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape) %>%
  mutate(sum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -SppType, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

ggplot(lspCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(lspCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Methods

Quick observations:

- Humans dominated by qualitative studies, with few empirical (i.e. few interviews, questionnaires?)
- Possibly surprisingly, plants do not have many RS studies

```{r}
methodsCounts <- sppdata %>%
  select(SppType, Empirical, Theoretical, Qualitative, Quantitative, GIS, `Remote sensing`) %>%
  mutate(sum = rowSums(.[2:7])) %>%
  gather(key = Type, value = count, -SppType, -sum) %>%
  mutate(prop = count / sum) 

ggplot(methodsCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(methodsCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Spatial Extent

Quick observations:

- Inverts dominated by mini studies
- Fish have relatively high proportion of Global studies
- Other species have reasonably evenly distributed proportions of scales
```{r}
spatialCounts <- sppdata %>%
  select(SppType, Micro, Mini, Local, Regional, National, Continental, Global,`Undefined Extent`) %>%
  mutate(sum = rowSums(.[2:9])) %>%
  gather(key = Type, value = count, -SppType, -sum) %>%
  mutate(prop = count / sum) 

ggplot(spatialCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(spatialCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Temporal Extent 

### With undefined

Quick observations:

- Difficult to see much; examine without 'undefined' 
```{r echo=F}
temporalCounts <- sppdata %>%
  select(SppType, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer, `Undefined Temporal`
) %>%
  mutate(sum = rowSums(.[2:10])) %>%
  gather(key = Type, value = count, -SppType, -sum) %>%
  mutate(prop = count / sum) 

ggplot(temporalCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(temporalCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

### Without Undefined

- Inverts dominated by annual (Yearly) studies, plus shorter studies
- Plants have greatest proportions of longer studies (Decadal and Centuries) - makes sense given rates of change? 
```{r echo=F}
temporalCounts <- sppdata %>%
  select(SppType, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer 
) %>%
  mutate(sum = rowSums(.[2:9])) %>%
  gather(key = Type, value = count, -SppType, -sum) %>%
  mutate(prop = count / sum) 

ggplot(temporalCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(temporalCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Concepts

Quick observations:

- Humans have a relatively large proportion of Ecosystem Services studies (not surprising?)
- Plants have largest number of LUCC studies
```{r}
conceptCounts <- sppdata %>%
  select(SppType, `PPS of landscapes`,
`Connectivity and fragmentation`, `Scale and scaling`,`Spatial analysis and modeling`,LUCC,`History and legacy`,`Climate change interactions`,`Ecosystem services`,`Landscape sustainability`,`Accuracy and uncertainty`
) %>%
  mutate(sum = rowSums(.[2:11])) %>%
  gather(key = Type, value = count, -SppType, -sum) %>%
  mutate(prop = count / sum) 

ggplot(conceptCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(conceptCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```


## Other Concepts

Quick observations:

- Humans have largest proportion of Cultural Landscapes, Socio-Economic and Planning studies (unsurprising?)
- Birds, Inverts and Mammals dominates by biodiveristy and Management and Conservation studies

```{r}
othCCounts <- sppdata %>%
  select(SppType, `Green Infrastructure`,`Planning and Architecture`,`Management and Conservation`,`Cultural Landscapes`,`Socio-economic Dimensions`,Biodiversity,`Landscape Assessment`,`Catchment Based Approach`,`Invasives Pests Diseases`
) %>%
  mutate(sum = rowSums(.[2:10])) %>%
  gather(key = Type, value = count, -SppType, -sum) %>%
  mutate(prop = count / sum) 

ggplot(othCCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(othCCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

