# Analysis by Organism

Bar charts to examine how contributions to conferences vary by organism

## Total Conference Contributions

```{r}
#spec(cpdata)

sppdata <- cpdata %>%
  select_if(is.numeric) %>%
  gather(key = SppType, value = count, Mammals:Fish) %>%
  filter(count > 0) %>%
  group_by(`SppType`) %>%
  summarise_all(sum, na.rm=T) 
```

Quick observations:

- Amphibians, Fish, Reptiles are little studied

```{r}

AsppCounts <- sppdata %>%
  select(SppType,Academic, Government,NGO,Business,Private) %>%
  mutate(Asum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -SppType, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(AsppCounts, aes(x=SppType, y=count)) + geom_bar(stat="identity")

```

## Author Affiliation

Quick observations:

- Businesses and private individuals study humans (proportional)
- By absolute numbers NGOs dominate study of birds 

```{r}
ggplot(AsppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(AsppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```


## Landscape Type 

### Using all landscape types

Quick observations: 

- Human studies are most evenly distributed across landscape types
- Unsurprisingly, fish are studies in riverscapes and seascapes
- Birds, plants and inverts studies dominated by Lowland rural studies

```{r}
lspsppCounts <- sppdata %>%
  select(SppType,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape, `Undefined LspType`,Other) %>%
  mutate(Asum = rowSums(.[2:8])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -SppType, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(lspsppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(lspsppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")
```

### Without 'Undefined LspType' and 'Other' landscape types

Quick observations:

- Birds, Plants and Mammals studies predominantly in Lowland Rural lsps
- Plants studies are grestest contribution (in total number) to Upland Rural lsps  

```{r}

lspsppCounts <- sppdata %>%
  select(SppType,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape) %>%
  mutate(Asum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -SppType, -Asum) %>%
  mutate(prop = count / Asum)  #calculate proportion

ggplot(lspsppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(lspsppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Methods

Quick observations:

- Humans dominated by qualitative studies, with few empirical (i.e. few interviews, questionnaires?)
- Possibly surprisingly, plants do not have many RS studies

```{r}
methodssppCounts <- sppdata %>%
  select(SppType, Empirical, Theoretical, Qualitative, Quantitative, GIS, `Remote sensing`) %>%
  mutate(yrsum = rowSums(.[2:7])) %>%
  gather(key = Type, value = count, -SppType, -yrsum) %>%
  mutate(prop = count / yrsum) 

ggplot(methodssppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(methodssppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Spatial Extent

Quick observations:

- Inverts dominated by mini studies
- Fish have relatively high proportion of Global studies
- Other species have reasonably evenly distributed proportions of scales
```{r}
extentsppCounts <- sppdata %>%
  select(SppType, Micro, Mini, Local, Regional, National, Continental, Global,`Undefined Extent`) %>%
  mutate(yrsum = rowSums(.[2:9])) %>%
  gather(key = Type, value = count, -SppType, -yrsum) %>%
  mutate(prop = count / yrsum) 

ggplot(extentsppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(extentsppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Temporal Extent 

### With undefined

Quick observations:

- Difficult to see much; examine without 'undefined' 
```{r echo=F}
temporalsppCounts <- sppdata %>%
  select(SppType, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer, `Undefined Temporal`
) %>%
  mutate(yrsum = rowSums(.[2:10])) %>%
  gather(key = Type, value = count, -SppType, -yrsum) %>%
  mutate(prop = count / yrsum) 

ggplot(temporalsppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(temporalsppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

### Without Undefined

- Inverts dominated by annual (Yearly) studies, plus shorter studies
- Plants have greatest proportions of longer studies (Decadal and Centuries) - makes sense given rates of change? 
```{r echo=F}
temporalsppCounts <- sppdata %>%
  select(SppType, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer 
) %>%
  mutate(yrsum = rowSums(.[2:9])) %>%
  gather(key = Type, value = count, -SppType, -yrsum) %>%
  mutate(prop = count / yrsum) 

ggplot(temporalsppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(temporalsppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Concepts

Quick observations:

- Humans have a relatively large proportion of Ecosystem Services studies (not surprising?)
- Plants have largest number of LUCC studies
```{r}
conceptsppCounts <- sppdata %>%
  select(SppType, `PPS of landscapes`,
`Connectivity and fragmentation`, `Scale and scaling`,`Spatial analysis and modeling`,LUCC,`History and legacy`,`Climate change interactions`,`Ecosystem services`,`Landscape sustainability`,`Accuracy and uncertainty`
) %>%
  mutate(yrsum = rowSums(.[2:11])) %>%
  gather(key = Type, value = count, -SppType, -yrsum) %>%
  mutate(prop = count / yrsum) 

ggplot(conceptsppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(conceptsppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```


## Other Concepts

Quick observations:

- Humans have largest proportion of Cultural Landscapes, Socio-Economic and Planning studies (unsurprising?)
- Birds, Inverts and Mammals dominates by biodiveristy and Management and Conservation studies

```{r}
othCsppCounts <- sppdata %>%
  select(SppType, `Green Infrastructure`,`Planning and Architecture`,`Management and Conservation`,`Cultural Landscapes`,`Socio-economic Dimensions`,Biodiversity,`Landscape Assessment`,`Catchment Based Approach`,`Invasives Pests Diseases`
) %>%
  mutate(yrsum = rowSums(.[2:10])) %>%
  gather(key = Type, value = count, -SppType, -yrsum) %>%
  mutate(prop = count / yrsum) 

ggplot(othCsppCounts, aes(x=SppType, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(othCsppCounts, aes(x=SppType, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

