# Analysis by Temporal Duration

Bar charts to examine how contributions to conferences vary by methods

```{r}
#spec(cpdata)

tempdata <- cpdata %>%
  select_if(is.numeric) %>%
  gather(key = Temporal, value = count, Hours:`Undefined Temporal`) %>%
  filter(count > 0) %>%
  group_by(`Temporal`) %>%
  summarise_all(sum, na.rm=T)

utempdata <- cpdata %>%
  select_if(is.numeric) %>%
  gather(key = Temporal, value = count, Hours:Longer) %>%
  filter(count > 0) %>%
  group_by(`Temporal`) %>%
  summarise_all(sum, na.rm=T) 

```

## Total Conference Contributions

Quick observations:

- Majority of studies do not define or report their temporal duration (65%)
- Those that do generally have durations longer than Years (~89%) 

```{r}

print(tempdata %>%
    select(Temporal, count) %>%
    mutate(prop = count/sum(count)) %>%
    mutate(prop = round(prop,3)))
    

ggplot(tempdata, aes(x=Temporal, y=count)) + 
  geom_bar(stat="identity") + 
  geom_text(aes(x=Temporal, y=max(count), label = paste0(round(100*count / sum(count),1), "%"), vjust=-0.5)) +
  ggtitle("All Data")


print(utempdata %>%
    select(Temporal, count) %>%
    mutate(prop = count/sum(count)) %>%
    mutate(prop = round(prop,3)))
    

ggplot(utempdata, aes(x=Temporal, y=count)) + 
  geom_bar(stat="identity") + 
  geom_text(aes(x=Temporal, y=max(count), label = paste0(round(100*count / sum(count),1), "%"), vjust=-0.5)) +
  ggtitle("Excluding Undefined")

```

## Author Affiliation

Quick observations:


```{r}

authCounts <- tempdata %>%
  select(Temporal,Academic, Government,NGO,Business,Private) %>%
  mutate(sum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -Temporal, -sum) %>%
  mutate(prop = count / sum) #calculate proportion 

authCountsW <- tempdata %>%
  select(Temporal,Academic, Government,NGO,Business,Private) %>%
  mutate(sum = rowSums(.[2:6])) %>%
  mutate_if(is.numeric, funs(prop = . / sum)) %>%
  mutate_at(8:12, round, 3)

print(authCountsW)

ggplot(authCounts, aes(x=Temporal, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(authCounts, aes(x=Temporal, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Landscape Type 

### Using all landscape types

Quick observations: 




```{r}
lspCounts <- tempdata %>%
  select(Temporal,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape, `Undefined LspType`,Other) %>%
  mutate(sum = rowSums(.[2:8])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -Temporal, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

ggplot(lspCounts, aes(x=Temporal, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(lspCounts, aes(x=Temporal, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")
```

### Without 'Undefined LspType' and 'Other' landscape types

Quick observations:


```{r}

lspCounts <- tempdata %>%
  select(Temporal,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape) %>%
  mutate(sum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -Temporal, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

ggplot(lspCounts, aes(x=Temporal, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(lspCounts, aes(x=Temporal, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

## Species

Quick observations


```{r}

speciesCounts <- tempdata %>%
  select(Temporal, Mammals, Humans, Birds, Reptiles, Inverts, Plants, Amphibians, Fish, `Generic Habitat`,`Woodland Forests`) %>%
  mutate(sum = rowSums(.[2:11])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -Temporal, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

ggplot(speciesCounts, aes(x=Temporal, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(speciesCounts, aes(x=Temporal, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```


## Methods

Quick observations:


```{r}
methodsCounts <- tempdata %>%
  select(Temporal, Empirical, Theoretical, Qualitative, Quantitative, GIS, `Remote sensing`) %>%
  mutate(sum = rowSums(.[2:7])) %>%
  gather(key = Type, value = count, -Temporal, -sum) %>%
  mutate(prop = count / sum) 

ggplot(methodsCounts, aes(x=Temporal, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(methodsCounts, aes(x=Temporal, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```



## Spatial Extent

Quick observations:



```{r}
extentCounts <- tempdata %>%
  select(Temporal, Micro, Mini, Local, Regional, National, Continental, Global,`Undefined Extent`) %>%
  mutate(sum = rowSums(.[2:9])) %>%
  gather(key = Type, value = count, -Temporal, -sum) %>%
  mutate(prop = count / sum) 

ggplot(extentCounts, aes(x=Temporal, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(extentCounts, aes(x=Temporal, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```



## Concepts

Quick observations:



```{r}
conceptCounts <- tempdata %>%
  select(Temporal, `PPS of landscapes`,
`Connectivity and fragmentation`, `Scale and scaling`,`Spatial analysis and modeling`,LUCC,`History and legacy`,`Climate change interactions`,`Ecosystem services`,`Landscape sustainability`,`Accuracy and uncertainty`
) %>%
  mutate(sum = rowSums(.[2:11])) %>%
  gather(key = Type, value = count, -Temporal, -sum) %>%
  mutate(prop = count / sum) 

ggplot(conceptCounts, aes(x=Temporal, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(conceptCounts, aes(x=Temporal, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```


## Other Concepts

Quick observations:



```{r}
otherCounts <- tempdata %>%
  select(Temporal, `Green Infrastructure`,`Planning and Architecture`,`Management and Conservation`,`Cultural Landscapes`,`Socio-economic Dimensions`,Biodiversity,`Landscape Assessment`,`Catchment Based Approach`,`Invasives Pests Diseases`
) %>%
  mutate(sum = rowSums(.[2:10])) %>%
  gather(key = Type, value = count, -Temporal, -sum) %>%
  mutate(prop = count / sum) 

ggplot(otherCounts, aes(x=Temporal, y=count, fill=Type)) + geom_bar(stat="identity", colour="white")

ggplot(otherCounts, aes(x=Temporal, y=prop, fill=Type)) + geom_bar(stat="identity", colour="white")

```

