# Analysis by Concept

Bar charts to examine how contributions to conferences vary by methods

```{r}
#spec(cpdata)

conceptdata <- cpdata %>%
  select_if(is.numeric) %>%
  gather(key = Concept, value = count, `PPS of landscapes`:`Accuracy and uncertainty`) %>%
  filter(count > 0) %>%
  group_by(`Concept`) %>%
  summarise_all(sum, na.rm=T) 

```

## Total Conference Contributions

Quick observations:

- Connectivity & fragmentation, LUCC and spatial analysis & modelling most frequent (composing > 50%) 

```{r}

#ggplot(authCounts, aes(x=Concept, y=count)) + geom_bar(stat="identity")

conceptdata %>%
  select(Concept, count) %>%
  mutate(prop = count/sum(count)) %>%
  mutate(prop = round(prop,3)) %>% 
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")
    

ggplot(conceptdata, aes(x=Concept, y=count)) + 
  geom_bar(stat="identity") + 
  geom_text(aes(x=Concept, y=max(count), label = paste0(round(100*count / sum(count),1), "%"), vjust=-0.25)) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```

## Author Affiliation

Quick observations:

- no obvious differences between concepts

```{r}
authCounts <- conceptdata %>%
  select(Concept,Academic, Government,NGO,Business,Private) %>%
  mutate(sum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -Concept, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

conceptdata %>%
  select(Concept,Academic, Government,NGO,Business,Private) %>%
  mutate(Total = rowSums(.[2:6])) %>%   #calculate total
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(authCounts, aes(x=Concept, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(authCounts, aes(x=Concept, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Landscape Type 

### Using all landscape types

Quick observations: 

- Ecosystem services have greatest proportion of urban landscapes and lowest in lowland rural
- Connectivity & Fragmentation have greatest proportion of studies in Lowland rural landscapes

```{r}
lspCounts <- conceptdata %>%
  select(Concept,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape, `Undefined LspType`,Other) %>%
  mutate(sum = rowSums(.[2:8])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -Concept, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

conceptdata %>%
  select(Concept,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape, `Undefined LspType`,Other) %>%
  mutate(Total = rowSums(.[2:8])) %>%   #calculate total
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(lspCounts, aes(x=Concept, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(lspCounts, aes(x=Concept, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Without 'Undefined LspType' and 'Other' landscape types

Quick observations:

- patterns seen above more obvious

```{r}

lspCounts <- conceptdata %>%
  select(Concept,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape) %>%
  mutate(sum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -Concept, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

conceptdata %>%
  select(Concept,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape) %>%
  mutate(Total = rowSums(.[2:6])) %>%   #calculate total
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(lspCounts, aes(x=Concept, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(lspCounts, aes(x=Concept, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Species

Quick observations

- Ecosystem services have greatest proportion of humans (31%)


```{r}

speciesCounts <- conceptdata %>%
  select(Concept, Mammals, Humans, Birds, Reptiles, Inverts, Plants, Amphibians, Fish, `Generic Habitat`,`Woodland Forests`) %>%
  mutate(sum = rowSums(.[2:11])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -Concept, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

conceptdata %>%
  select(Concept, Mammals, Humans, Birds, Reptiles, Inverts, Plants, Amphibians, Fish, `Generic Habitat`,`Woodland Forests`) %>%
  mutate(Total = rowSums(.[2:11])) %>%   #calculate total for subsquent calcultation of proportion
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(speciesCounts, aes(x=Concept, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(speciesCounts, aes(x=Concept, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


## Methods

Quick observations:

- Ecosystem services has smallest proportion of Empirical studies

```{r}
methodsCounts <- conceptdata %>%
  select(Concept, Empirical, Theoretical, Qualitative, Quantitative, GIS, `Remote sensing`) %>%
  mutate(sum = rowSums(.[2:7])) %>%
  gather(key = Type, value = count, -Concept, -sum) %>%
  mutate(prop = count / sum) 

conceptdata %>%
  select(Concept, Empirical, Theoretical, Qualitative, Quantitative, GIS, `Remote sensing`) %>%
  mutate(Total = rowSums(.[2:7])) %>%
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(methodsCounts, aes(x=Concept, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(methodsCounts, aes(x=Concept, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```



## Spatial Extent

Quick observations:

- Ecosystem services has the largest proportion of global studies and fewest mini and micro studies
- Connectivity & Fragmentation has largest proportion of local studies

```{r}
spatialCounts <- conceptdata %>%
  select(Concept, Micro, Mini, Local, Regional, National, Continental, Global,`Undefined Extent`) %>%
  mutate(sum = rowSums(.[2:9])) %>%
  gather(key = Type, value = count, -Concept, -sum) %>%
  mutate(prop = count / sum) 

conceptdata %>%
  select(Concept, Micro, Mini, Local, Regional, National, Continental, Global,`Undefined Extent`) %>%
  mutate(Total = rowSums(.[2:9])) %>%
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(spatialCounts, aes(x=Concept, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(spatialCounts, aes(x=Concept, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```



## Temporal Extent 

### With undefined

Quick observations:


```{r echo=F}
temporalCounts <- conceptdata %>%
  select(Concept, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer, `Undefined Temporal`
) %>%
  mutate(sum = rowSums(.[2:10])) %>%
  gather(key = Type, value = count, -Concept, -sum) %>%
  mutate(prop = count / sum) 

conceptdata %>%
  select(Concept, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer, `Undefined Temporal`
) %>%
  mutate(Total = rowSums(.[2:10])) %>%
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(temporalCounts, aes(x=Concept, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(temporalCounts, aes(x=Concept, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

### Without Undefined

- History and Legacy studies have greatest proportion of Centries and Longer studies


```{r echo=F}
temporalCounts <- conceptdata %>%
  select(Concept, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer 
) %>%
  mutate(sum = rowSums(.[2:9])) %>%
  gather(key = Type, value = count, -Concept, -sum) %>%
  mutate(prop = count / sum) 

conceptdata %>%
  select(Concept, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer 
) %>%
  mutate(Total = rowSums(.[2:9])) %>%
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(temporalCounts, aes(x=Concept, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(temporalCounts, aes(x=Concept, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```



## Other Concepts

Quick observations:

- Connectivity & Fragmentation and pattern-process-scale have greatest proportion of biodiversity studies
- History and Legacy have greatest proportion of cultural studies

```{r}
otherCounts <- conceptdata %>%
  select(Concept, `Green Infrastructure`,`Planning and Architecture`,`Management and Conservation`,`Cultural Landscapes`,`Socio-economic Dimensions`,Biodiversity,`Landscape Assessment`,`Catchment Based Approach`,`Invasives Pests Diseases`
) %>%
  mutate(sum = rowSums(.[2:10])) %>%
  gather(key = Type, value = count, -Concept, -sum) %>%
  mutate(prop = count / sum) 

conceptdata %>%
  select(Concept, `Green Infrastructure`,`Planning and Architecture`,`Management and Conservation`,`Cultural Landscapes`,`Socio-economic Dimensions`,Biodiversity,`Landscape Assessment`,`Catchment Based Approach`,`Invasives Pests Diseases`
) %>%
  mutate(Total = rowSums(.[2:10])) %>%
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(otherCounts, aes(x=Concept, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(otherCounts, aes(x=Concept, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

