# Analysis by Other Concepts

Bar charts to examine how contributions to conferences vary by methods

```{r}
#spec(cpdata)

othdata <- cpdata %>%
  select_if(is.numeric) %>%
  gather(key = OtherC, value = count, `Green Infrastructure`:`Invasives Pests Diseases`) %>%
  filter(count > 0) %>%
  group_by(`OtherC`) %>%
  summarise_all(sum, na.rm=T) 

```

## Total Conference Contributions

Quick observations:

- invasive pests have smallest number of studies (and therefore treat qualitative differences in proportions below with caution)
- Management & Conservation and Biodiversity studies componse the majority of studies (56%)

```{r}
othdata %>%
  select(OtherC, count) %>%
  mutate(prop = count/sum(count)) %>%
  mutate(prop = round(prop,3)) %>% 
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")
    

ggplot(othdata, aes(x=OtherC, y=count)) + 
  geom_bar(stat="identity") + 
  geom_text(aes(x=OtherC, y=max(count), label = paste0(round(100*count / sum(count),1), "%"), vjust=-0.25)) + 
  theme(axis.text.x = element_text(angle = 25, hjust = 1))

```

## Author Affiliation

Quick observations:

- no obvious differences (thother than invasive pests which has small numbers)

```{r}
authCounts <- othdata %>%
  select(OtherC,Academic, Government,NGO,Business,Private) %>%
  mutate(sum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -OtherC, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

othdata %>%
  select(OtherC,Academic, Government,NGO,Business,Private) %>%
  mutate(Total = rowSums(.[2:6])) %>%   #calculate total
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(authCounts, aes(x=OtherC, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(authCounts, aes(x=OtherC, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Landscape Type 

### Using all landscape types

Quick observations: 

- Green infrastructure has by far greatest proportion of Urban landscape studies (makes sense)
- Catchment approaches have greatest proportion of Riverscapes (makes sense)

```{r}
lspCounts <- othdata %>%
  select(OtherC,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape, `Undefined LspType`,Other) %>%
  mutate(sum = rowSums(.[2:8])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -OtherC, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

othdata %>%
  select(OtherC,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape, `Undefined LspType`,Other) %>%
  mutate(Total = rowSums(.[2:8])) %>%   #calculate total
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(lspCounts, aes(x=OtherC, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(lspCounts, aes(x=OtherC, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Without 'Undefined LspType' and 'Other' landscape types

Quick observations:

- as above

```{r}

lspCounts <- othdata %>%
  select(OtherC,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape) %>%
  mutate(sum = rowSums(.[2:6])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -OtherC, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

othdata %>%
  select(OtherC,`Upland rural`, `Lowland rural`, Urban,	Riverscape, Seascape) %>%
  mutate(Total = rowSums(.[2:6])) %>%   #calculate total
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(lspCounts, aes(x=OtherC, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(lspCounts, aes(x=OtherC, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Species

Quick observations

- Management & Conservation studies have relatively low propotion of human studies; greatest proportion of Woodland studies
- Biodiversity studies have relatively large proportion of Inverts (along with invasives)

```{r}

speciesCounts <- othdata %>%
  select(OtherC, Mammals, Humans, Birds, Reptiles, Inverts, Plants, Amphibians, Fish, `Generic Habitat`,`Woodland Forests`) %>%
  mutate(sum = rowSums(.[2:11])) %>%   #calculate total for subsquent calcultation of proportion
  gather(key = Type, value = count, -OtherC, -sum) %>%
  mutate(prop = count / sum)  #calculate proportion

othdata %>%
  select(OtherC, Mammals, Humans, Birds, Reptiles, Inverts, Plants, Amphibians, Fish, `Generic Habitat`,`Woodland Forests`) %>%
  mutate(Total = rowSums(.[2:11])) %>%   #calculate total for subsquent calcultation of proportion
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(speciesCounts, aes(x=OtherC, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(speciesCounts, aes(x=OtherC, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


## Methods

Quick observations:

- Other than invasives, Biodiversity and Management & Conservation have greatest proportions of Empirical and lowest proportions of Theoretical


```{r}
methodsCounts <- othdata %>%
  select(OtherC, Empirical, Theoretical, Qualitative, Quantitative, GIS, `Remote sensing`) %>%
  mutate(sum = rowSums(.[2:7])) %>%
  gather(key = Type, value = count, -OtherC, -sum) %>%
  mutate(prop = count / sum) 

othdata %>%
  select(OtherC, Empirical, Theoretical, Qualitative, Quantitative, GIS, `Remote sensing`) %>%
  mutate(Total = rowSums(.[2:7])) %>%
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(methodsCounts, aes(x=OtherC, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(methodsCounts, aes(x=OtherC, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


## Spatial Extent

Quick observations:



```{r}
spatialCounts <- othdata %>%
  select(OtherC, Micro, Mini, Local, Regional, National, Continental, Global,`Undefined Extent`) %>%
  mutate(sum = rowSums(.[2:9])) %>%
  gather(key = Type, value = count, -OtherC, -sum) %>%
  mutate(prop = count / sum) 

othdata %>%
  select(OtherC, Micro, Mini, Local, Regional, National, Continental, Global,`Undefined Extent`) %>%
  mutate(Total = rowSums(.[2:9])) %>%
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(spatialCounts, aes(x=OtherC, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(spatialCounts, aes(x=OtherC, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


## Temporal Extent 

### With undefined

Quick observations:

- no obvious patterns

```{r echo=F}
temporalCounts <- othdata %>%
  select(OtherC, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer, `Undefined Temporal`
) %>%
  mutate(sum = rowSums(.[2:10])) %>%
  gather(key = Type, value = count, -OtherC, -sum) %>%
  mutate(prop = count / sum) 

othdata %>%
  select(OtherC, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer, `Undefined Temporal`
) %>%
  mutate(Total = rowSums(.[2:10])) %>%
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(temporalCounts, aes(x=OtherC, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(temporalCounts, aes(x=OtherC, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

### Without Undefined

- no obvious patterns

```{r echo=F}
temporalCounts <- othdata %>%
  select(OtherC, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer 
) %>%
  mutate(sum = rowSums(.[2:9])) %>%
  gather(key = Type, value = count, -OtherC, -sum) %>%
  mutate(prop = count / sum) 

othdata %>%
  select(OtherC, Hours, Days, Weeks, Months, Years, Decades, Centuries, Longer 
) %>%
  mutate(Total = rowSums(.[2:9])) %>%
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(temporalCounts, aes(x=OtherC, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(temporalCounts, aes(x=OtherC, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Concepts

Quick observations:

- Biodiversity and Management & Conservation have similar proportions; both with relatively large proportions of connectivity and fragmentation

```{r}
conceptCounts <- othdata %>%
  select(OtherC, `PPS of landscapes`,
`Connectivity and fragmentation`, `Scale and scaling`,`Spatial analysis and modeling`,LUCC,`History and legacy`,`Climate change interactions`,`Ecosystem services`,`Landscape sustainability`,`Accuracy and uncertainty`
) %>%
  mutate(sum = rowSums(.[2:11])) %>%
  gather(key = Type, value = count, -OtherC, -sum) %>%
  mutate(prop = count / sum) 


othdata %>%
  select(OtherC, `PPS of landscapes`,
`Connectivity and fragmentation`, `Scale and scaling`,`Spatial analysis and modeling`,LUCC,`History and legacy`,`Climate change interactions`,`Ecosystem services`,`Landscape sustainability`,`Accuracy and uncertainty`
) %>%
  mutate(Total = rowSums(.[2:11])) %>%
  mutate_if(is.numeric, funs(prop = ./ Total)) %>%
  mutate_at(vars(ends_with("prop")), round, 3) %>% 
  select(-Total_prop) %>%
  kable() %>%
  kable_styling() %>%
  scroll_box(width = "100%")

ggplot(conceptCounts, aes(x=OtherC, y=count, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

ggplot(conceptCounts, aes(x=OtherC, y=prop, fill=Type)) + 
  geom_bar(stat="identity", colour="white") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

